Estimating real-time high street footfall from Wi-Fi probe requests

### 2018-01-31 abstract.tex
Fixed figure reference

	\begin{figure*}
		\begin{center}
			\includegraphics
				[width=0.8\textwidth,trim=4 4 4 4,clip]
				{outputs/clustering_2.png}
			\caption{Clustering probe requests based on increasing sequence
			numbers present in them.}
			label{fig}
		\end{center}
	\end{figure*}

@@

	The nodes are then classified based on the unique connected component they
	belong to. This classification is assigned as the unique identifier for the
	anonymised probe requests.
	\ref{fig} shows the clustering process for where the black dots show
	probe requests and red lines connecting them show the clusters
	corresponding to the same device generated them.
	We finally combine both normal and anonymised probe requests, 
	aggregate them based on their unique identifier and remove
	repeating probe requests which reduces the difference between
	the sensor counts and the manual counts to -18\%.

>>>>

	\begin{figure*}
		\begin{center}
			\includegraphics
				[width=0.8\textwidth,trim=4 4 4 4,clip]
				{outputs/clustering_2.png}
			\caption{Clustering probe requests based on increasing sequence
			numbers present in them.}
			\label{fig}
		\end{center}
	\end{figure*}

@@

	The nodes are then classified based on the unique connected component they
	belong to. This classification is assigned as the unique identifier for the
	anonymised probe requests.
	Figure \ref{fig} shows the clustering process for where the black dots show
	probe requests and red lines connecting them show the clusters
	corresponding to the same device generated them.
	We finally combine both normal and anonymised probe requests, 
	aggregate them based on their unique identifier and remove
	repeating probe requests which reduces the difference between
	the sensor counts and the manual counts to -18\%.
